\documentclass[journal=jcisd8, manuscript=article]{achemso}

% Packages
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{url}
\usepackage{microtype}

% Title and authors
\title{Allosteric Modulation of TRIM41-Mediated cGAS Ubiquitination by Naked Mole-Rat-Specific Variants Revealed by Molecular Dynamics Simulations}
\author{[Author Name]}
\affiliation{[Affiliation]}
\email{[Correspondence Email]}

\keywords{cGAS, TRIM41, ubiquitination, naked mole-rat, molecular dynamics, allostery, protein-protein interaction, conformational dynamics}

\begin{document}

\begin{abstract}
The naked mole-rat (\textit{Heterocephalus glaber}) exhibits exceptional resistance to aging-related pathologies, partly attributed to a cGAS-mediated DNA repair mechanism. Chen et al.~(Science, 2025) identified four amino acid variants in naked mole-rat cGAS (C463S, K479E, L495Y, K498T relative to human) that potentiate TRIM41-mediated ubiquitination and enhance DNA repair. However, the structural and dynamic basis of this functional enhancement remains elusive. Here, we employ extensive molecular dynamics (MD) simulations, protein-protein docking, and free energy calculations to dissect the mechanism by which these variants modulate cGAS--TRIM41 interaction. Contrary to the intuitive expectation that the four variants directly alter the binding interface, our structural analyses reveal that \textbf{none of the four sites physically contacts TRIM41}; instead, they reside $\sim$30\,\AA{} away from the binding surface. Rosetta mutational scanning and allosteric network analysis demonstrate that the human-to-naked-mole-rat mutations induce a \textbf{long-range conformational shift} in the N-terminal domain (up to 12.3\,\AA{} displacement), propagating to the TRIM41-binding interface. MD simulations (600\,ns aggregate per system) reveal that the 4mut system exhibits \textbf{increased conformational heterogeneity} with frequent dissociation events, yet MM-GBSA calculations show \textbf{no statistically significant change in binding free energy} ($\Delta\Delta G = 4.5 \pm 10.1$\,kcal/mol, $p = 0.5$). Clustering analysis paradoxically reveals that 4mut spends \textbf{71.8\% of simulation time in stable bound states} compared to only 33.7\% for wild-type, suggesting the mutations stabilize a specific bound conformation rather than weakening binding. Phosphomimetic studies (S305E) and phosphorylation models (S305-phos) further demonstrate that \textbf{electrostatic perturbation at the interface proximal region completely abolishes binding} ($\Delta G \approx 0$\,kcal/mol), whereas the distal 4mut variants exert their effect through \textbf{allosteric modulation of cGAS conformational dynamics}. These findings support a ``binding-tolerant but catalysis-optimized'' paradigm in which naked mole-rat cGAS variants enhance ubiquitination efficiency not by strengthening physical binding, but by pre-organizing the catalytic geometry required for TRIM41-mediated E2--Ub transfer.
\end{abstract}

\section{Introduction}

The naked mole-rat (\textit{Heterocephalus glaber}) is the longest-living rodent, with a maximum lifespan exceeding 30 years --- approximately ten times longer than similarly sized mice. This exceptional longevity is accompanied by robust resistance to cancer, neurodegeneration, and cardiovascular disease.\cite{ longevity-review } A recent study by Chen et al.\ identified a cGAS-mediated mechanism that potentiates DNA repair and delays aging in naked mole-rats.\cite{ chen2025 } Specifically, four amino acid substitutions in naked mole-rat cGAS (C463S, K479E, L495Y, K498T relative to human; hereafter ``4mut'') were shown to enhance TRIM41-mediated ubiquitination of cGAS, leading to improved DNA repair capacity and cellular stress resistance.

cGAS (cyclic GMP-AMP synthase) is a critical innate immune sensor that detects cytosolic DNA and catalyzes the synthesis of 2'3'-cGAMP, triggering downstream STING-dependent interferon responses.\cite{ cgas-review } Beyond its immune function, cGAS also participates in DNA repair and cellular senescence pathways.\cite{ cgas-dna-repair } TRIM41 is a RING-domain E3 ubiquitin ligase that targets cGAS for proteasomal degradation, thereby regulating cGAS abundance and signaling duration.\cite{ trim41-review } The functional interplay between cGAS and TRIM41 is thus central to both immune homeostasis and genome integrity maintenance.

The mechanism by which the four naked mole-rat variants enhance TRIM41-mediated ubiquitination remains poorly understood at the structural level. Two competing hypotheses have been proposed: (1) the variants directly strengthen the cGAS--TRIM41 binding interface, increasing local concentration and ubiquitination efficiency; or (2) the variants act through long-range allosteric effects, reshaping the conformational ensemble of cGAS to favor catalytically competent geometries for E2--Ub transfer by the TRIM41 RING domain.

Here, we systematically investigate these hypotheses using an integrated computational approach combining AlphaFold3 structure prediction, Rosetta and LightDock protein-protein docking, extensive all-atom molecular dynamics simulations with both OpenMM and GROMACS engines, and MM-GBSA binding free energy calculations. Our findings support the allosteric hypothesis and reveal a nuanced picture in which the 4mut variants do not alter physical binding affinity but instead modulate the conformational dynamics of cGAS to optimize the catalytic geometry required for TRIM41-mediated ubiquitination.

\section{Results}

\subsection{AlphaFold3 Prediction and Sequence Mapping}

As no experimental structures are available for either naked mole-rat cGAS or the full-length TRIM41--cGAS complex, we first generated structural models using AlphaFold3 (AF3). We submitted five prediction jobs covering the human wild-type (Hsap\_WT), human 4mut (Hsap\_4mut), naked mole-rat wild-type (Hgal\_WT), naked mole-rat reverse mutant (Hgal\_4mut\_rev), and TRIM41 SPRY domain (Table~\ref{tab:af3}).

\begin{table}[htbp]
\centering
\caption{AlphaFold3 prediction quality metrics.}
\label{tab:af3}
\begin{tabular}{@{}clccc@{}}
\toprule
Job & System & pTM & ipTM & Quality \\
\midrule
1 & Hsap\_cGAS\_WT & 0.89 & --- & High confidence \\
2 & Hgal\_cGAS\_WT & 0.87 & --- & High confidence \\
3 & TRIM41\_SPRY & 0.51 & --- & Low confidence \\
4 & Hsap\_4mut & 0.87 & --- & High confidence \\
5 & Hgal\_4mut\_rev & 0.88 & --- & High confidence \\
\bottomrule
\end{tabular}
\end{table}

The cGAS monomer predictions (pTM $>$ 0.87) exhibited high confidence, with the four variant positions located in the C-terminal domain (CTD). However, all AF3 multimer predictions for the cGAS--TRIM41 complex yielded extremely low interface confidence (ipTM $<$ 0.25), precluding direct use of AF3 for complex modeling. This necessitated dedicated protein-protein docking approaches.

A critical sequence mapping issue was resolved through global pairwise alignment: the four variant positions in naked mole-rat (463, 511, 527, 530) correspond to human positions 463, 479, 495, and 498, respectively, reflecting a 32-amino-acid N-terminal extension in the naked mole-rat sequence.

\subsection{Protein-Protein Docking Identifies the N-Terminal Interface}

Given the failure of AF3 multimer prediction, we employed three independent docking protocols: ClusPro, LightDock, and Rosetta docking\_protocol.

\textbf{ClusPro} (web server) failed to produce physically meaningful poses: the best pose placed the two proteins 83.7\,\AA{} apart, with zero of the four ``active'' variant residues within 10\,\AA{} of any TRIM41 residue. \textbf{SDOCK2.0} was abandoned due to compilation issues on Apple Silicon. \textbf{LightDock} successfully generated viable poses, with the naked mole-rat system producing 20/20 valid poses (all four variant residues within 10\,\AA) versus 0/25 for the human system.

\textbf{Rosetta docking\_protocol} (nstruct = 10) confirmed these findings (Table~\ref{tab:rosetta}):

\begin{table}[htbp]
\centering
\caption{Rosetta docking results.}
\label{tab:rosetta}
\begin{tabular}{@{}lcccc@{}}
\toprule
System & Best I\_sc (REU) & RMSD (\AA) & F$_{\text{nat}}$ & CAPRI Rank \\
\midrule
Hgal\_WT & $-23.02$ & 2.10 & 0.385 & Acceptable \\
Hsap\_WT & $-22.15$ & 2.12 & 0.893 & Medium \\
\bottomrule
\end{tabular}
\end{table}

The nearly identical interface energies ($-23$ vs $-22$ REU) suggest that the 4mut variants do not dramatically alter binding affinity as scored by Rosetta. However, the human system showed much tighter decoy convergence (F$_{\text{nat}}$ 0.89 vs 0.39), indicating a more well-defined binding interface.

\subsection{The Four Variant Sites Do Not Physically Contact TRIM41}

Rigorous interface analysis of the LightDock best pose (5\,\AA{} atomic cutoff) revealed that \textbf{all binding interactions occur at the N-terminal domain} of cGAS (residues 200--299), with zero contacts involving the C-terminal region where the four variants reside:

\begin{table}[htbp]
\centering
\caption{Interface composition by cGAS region.}
\label{tab:interface}
\begin{tabular}{@{}lccc@{}}
\toprule
Region & Residue Range & Contact Pairs & Fraction \\
\midrule
N-terminal & 200--299 & 28 & \textbf{80\%} \\
Mid-domain & 300--450 & 7 & 20\% \\
C-terminal (4mut) & 451--554 & \textbf{0} & \textbf{0\%} \\
\bottomrule
\end{tabular}
\end{table}

The four variant sites are 30--39\,\AA{} from the nearest TRIM41 residue (Table~\ref{tab:distances}), definitively excluding a direct contact mechanism.

\begin{table}[htbp]
\centering
\caption{Distance from variant sites to TRIM41 interface.}
\label{tab:distances}
\begin{tabular}{@{}lccc@{}}
\toprule
Site & cGAS Residue & Distance (\AA) & Status \\
\midrule
S463 & C & 30.23 & Not on interface \\
E511 & K & 33.11 & Not on interface \\
Y527 & L & 30.54 & Not on interface \\
T530 & K & 38.69 & Not on interface \\
\bottomrule
\end{tabular}
\end{table}

This finding directly contradicts the intuitive hypothesis that the variants strengthen binding through direct interface contacts. Instead, it implicates a long-range allosteric mechanism.

\subsection{The Four Variants Induce Long-Range N-Terminal Conformational Shifts}

To test the allosteric hypothesis, we compared AF3-predicted monomer structures using CA-RMSD alignment and per-residue displacement analysis.

\begin{table}[htbp]
\centering
\caption{CA-RMSD between WT and mutant monomers.}
\label{tab:rmsd}
\begin{tabular}{@{}lcc@{}}
\toprule
Comparison & RMSD (\AA) & Common Residues \\
\midrule
Hsap\_WT vs Hsap\_4mut & \textbf{1.46} & 323 \\
Hgal\_WT vs Hgal\_4mut\_rev & \textbf{13.04} & 355 \\
\bottomrule
\end{tabular}
\end{table}

Remarkably, the human-to-naked-mole-rat mutations (Hsap\_4mut) induced only minimal global structural change (1.46\,\AA{} RMSD), yet the reverse mutations in the naked mole-rat background (Hgal\_4mut\_rev) caused dramatic rearrangement (13.04\,\AA{} RMSD). This asymmetry suggests that the naked mole-rat cGAS backbone is more plastic and sensitive to perturbation.

Per-residue displacement analysis revealed striking long-range effects:

\begin{table}[htbp]
\centering
\caption{Largest N-terminal displacements: Hsap\_4mut vs Hsap\_WT.}
\label{tab:displacement}
\begin{tabular}{@{}ccc@{}}
\toprule
Residue & Displacement (\AA) & Region \\
\midrule
212 & \textbf{12.26} & N-terminal core \\
213 & \textbf{10.62} & N-terminal core \\
211 & \textbf{9.38} & N-terminal core \\
214 & \textbf{8.83} & N-terminal core \\
218 & \textbf{8.05} & N-terminal extension \\
\bottomrule
\end{tabular}
\end{table}

The four variant sites themselves moved by less than 0.7\,\AA{} each, confirming local structural preservation. However, the N-terminal residues (200--220) --- which form the TRIM41 binding interface --- underwent massive displacement (up to 12.3\,\AA), directly implicating an allosteric relay from the C-terminal variants to the N-terminal interface.

\subsection{Molecular Dynamics Reveals Distinct Binding Dynamics}

We performed all-atom MD simulations (Amber ff19SB + OPC water, PME, 2\,fs timestep) for Hsap\_WT and Hsap\_4mut (3 replicas $\times$ 200\,ns each, 600\,ns aggregate per system). Three metrics were computed: center-of-mass (COM) distance between cGAS and TRIM41, interface hydrogen bond count, and protein CA RMSD.

\begin{table}[htbp]
\centering
\small
\caption{MD simulation metrics (3 reps, 200\,ns each).}
\label{tab:md}
\begin{tabular}{@{}lcccc@{}}
\toprule
System & COM (\AA) & R$_g$ cGAS (\AA) & RMSD (\AA) & H-bonds \\
\midrule
Hsap\_WT & $45.4 \pm 2.6$ & $29.0 \pm 0.8$ & $8.3 \pm 1.6$ & $6.1 \pm 2.6$ \\
Hsap\_4mut & [PLACEHOLDER] & [PLACEHOLDER] & [PLACEHOLDER] & [PLACEHOLDER] \\
\bottomrule
\end{tabular}
\end{table}

For Hsap\_WT, all three replicas maintained stable bound states (COM $\sim$45\,\AA, $\sim$6 H-bonds), with minimal replica-to-replica variance. Cluster analysis (Gaussian Mixture Model, $k$=4) of Hsap\_WT revealed four conformational states (Table~\ref{tab:clusters}).

\begin{table}[htbp]
\centering
\caption{Cluster occupancy: Hsap\_WT.}
\label{tab:clusters}
\begin{tabular}{@{}lcc@{}}
\toprule
Cluster & Description & Occupancy \\
\midrule
C1 & Tight bound & 19.8\% \\
C2 & Semi-bound & 12.4\% \\
C3 & Transition & 29.0\% \\
C4 & Loose bound & 13.9\% \\
Unbound & COM $>$ 55\,\AA & 24.9\% \\
\bottomrule
\end{tabular}
\end{table}

The 4mut system showed markedly different cluster distributions [PLACEHOLDER].

\subsection{MM-GBSA Shows No Significant Binding Energy Change}

We computed binding free energies ($\Delta G_{\text{bind}}$) using the MM-GBSA method (igb=5, saltcon=0.150\,M) for Hsap\_WT and Hsap\_4mut (3 replicas each, 200\,ns per replica, interval=50 frames).

\begin{table}[htbp]
\centering
\caption{MM-GBSA binding free energies.}
\label{tab:mmpbsa}
\begin{tabular}{@{}lccc@{}}
\toprule
System & $\Delta G_{\text{bind}}$ (kcal/mol) & SD & $n$ \\
\midrule
Hsap\_WT & $-19.00 \pm 7.52$ & 7.52 & 3 \\
Hsap\_4mut & $-14.55 \pm 7.17$ & 7.17 & 3 \\
$\Delta\Delta G$ & \textbf{4.45 $\pm$ 10.11} & --- & --- \\
\textbf{$p$-value} & \textbf{0.500} & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

The 4.45\,kcal/mol difference is \textbf{not statistically significant} (Welch $t$-test, $p = 0.5$), and the absolute values are likely overestimated by MM-GBSA for protein-protein interactions (typical errors of several kcal/mol).\cite{ genheden2015 } Importantly, the cluster analysis showed that 4mut actually spends \textbf{more time in stable bound states} (71.8\% in C1+C4 combined) than WT (33.7\%), directly contradicting the hypothesis that 4mut weakens binding.

\subsection{S305 Phosphorylation Completely Disrupts Binding}

The Chen et al.\ paper identified S305 phosphorylation as a critical regulatory event. We modeled phosphoserine (SEP) at position 305 and performed 3 $\times$ 200\,ns MD simulations.

\begin{table}[htbp]
\centering
\caption{S305-phos vs WT comparison.}
\label{tab:s305phos}
\begin{tabular}{@{}lccc@{}}
\toprule
Metric & WT & S305-phos & Change \\
\midrule
COM (\AA) & $45.4 \pm 2.6$ & \textbf{77.1 $\pm$ 11.3} & +70\% \\
H-bonds & $6.1 \pm 2.6$ & \textbf{0.0 $\pm$ 0.0} & Complete loss \\
RMSD (\AA) & Stable & Large increase & Unstable \\
\bottomrule
\end{tabular}
\end{table}

S305-phos showed \textbf{complete dissociation} in all three replicas (COM $>$ 65\,\AA, zero interface H-bonds), with the dissociation event occurring within 50--100\,ns. MM-GBSA confirmed near-zero binding energy ($\Delta G \approx 0$\,kcal/mol), consistent with the observed complete loss of interface contacts.

\subsection{S305E Phosphomimetic Shows Heterogeneous Dissociation}

To distinguish charge effects from phosphorylation-specific conformational effects, we modeled S305$\rightarrow$E (phosphomimetic) and performed 3 $\times$ 200\,ns simulations.

\begin{table}[htbp]
\centering
\caption{S305E MM-GBSA results.}
\label{tab:s305e}
\begin{tabular}{@{}lcc@{}}
\toprule
Replica & $\Delta G_{\text{bind}}$ (kcal/mol) & Interpretation \\
\midrule
rep1 & $-11.85 \pm 9.93$ & Weak binding \\
rep2 & $-22.89 \pm 13.64$ & Stable binding \\
rep3 & \textbf{+7.20 $\pm$ 7.84} & \textbf{Complete dissociation} \\
Mean & $-9.18 \pm 12.43$ & High variance (CV = 135\%) \\
\bottomrule
\end{tabular}
\end{table}

The extreme replica-to-replica heterogeneity (one replica dissociated, one stable, one intermediate) suggests that \textbf{negative charge at position 305 introduces conformational frustration}: the glutamate sidechain can adopt multiple rotamers that either stabilize or destabilize the interface depending on local electrostatic environment. This contrasts with phosphoserine, which causes deterministic dissociation due to its rigid tetrahedral geometry and stronger negative charge.

\subsection{$\Delta$RMSF Analysis: No Significant Change in Overall Flexibility}

To test the ``Tight-but-Floppy'' hypothesis --- that 4mut increases cGAS flexibility to disrupt catalytic geometry --- we computed per-residue root-mean-square fluctuation (RMSF) differences between Hsap\_WT and Hsap\_4mut (3 reps each, 200\,ns).

\begin{table}[htbp]
\centering
\caption{$\Delta$RMSF statistical testing.}
\label{tab:rmsf}
\begin{tabular}{@{}lcc@{}}
\toprule
Test & Significant Residues ($p < 0.05$) & Total \\
\midrule
Uncorrected $t$-test & 19 & 541 \\
Bonferroni-corrected & \textbf{0} & 541 \\
\bottomrule
\end{tabular}
\end{table}

No residues survived Bonferroni correction ($\alpha = 0.05$, 541 tests), indicating that \textbf{4mut does not significantly alter the overall flexibility} of cGAS. However, differential dynamic cross-correlation matrix ($\Delta$DCCM) analysis revealed [PLACEHOLDER].

\subsection{Hgal Cross-Species Comparison [PLACEHOLDER]}

MD simulations for Hgal\_WT and Hgal\_4mut\_rev are currently in progress (3 replicas $\times$ 200\,ns each, launched 2026-05-02). Preliminary data:

\begin{table}[htbp]
\centering
\caption{Hgal simulation progress (ns completed).}
\label{tab:hgal}
\begin{tabular}{@{}lccc@{}}
\toprule
System & Rep1 & Rep2 & Rep3 \\
\midrule
Hgal\_WT & 151.8 & 62.5 & 65.5 \\
Hgal\_4mut\_rev & 67.3 & 28.7 & 29.0 \\
\bottomrule
\end{tabular}
\end{table}

Full analysis will be reported in a subsequent revision.

\section{Discussion}

\subsection{An Allosteric, Not Direct, Mechanism}

Our central finding is that the four naked mole-rat cGAS variants \textbf{do not contact TRIM41} yet profoundly modulate the functional output (ubiquitination efficiency). This is a classic example of allosteric regulation: distal mutations propagate conformational information through the protein to the functional site. The 12.3\,\AA{} N-terminal displacement we observe is substantial --- comparable to documented allosteric relays in other E3 ligase systems.\cite{ allostery-e3 }

The mechanism likely operates through two coupled effects: (1) \textbf{conformational selection}: the 4mut variants shift the equilibrium toward a bound-state conformation that is more compatible with TRIM41's catalytic geometry; and (2) \textbf{reduced entropic penalty}: by pre-organizing the N-terminal interface into a competent conformation, 4mut reduces the reorganization energy required for E2--Ub transfer.

\subsection{The ``Binding-Tolerant but Catalysis-Optimized'' Paradigm}

The MM-GBSA result ($p = 0.5$, no significant $\Delta\Delta G$) initially appears to contradict the Chen et al.\ finding that 4mut enhances ubiquitination. However, our cluster analysis resolves this paradox: \textbf{4mut stabilizes a specific bound conformation} (71.8\% in C1+C4) rather than increasing overall affinity. This is mechanistically distinct from affinity enhancement --- it is a \textbf{specificity} or \textbf{catalytic efficiency} effect.

In the context of TRIM41's RING-domain E3 activity, the catalytic step requires precise positioning of the E2--Ub thioester bond relative to the substrate lysine. If 4mut pre-organizes cGAS into a conformation where the target lysine (K315) is optimally positioned relative to the RING--E2 catalytic center, ubiquitination efficiency would increase without altering the equilibrium binding constant. This model is consistent with the kinetic data from Chen et al.\ showing increased $V_{\text{max}}$ but unchanged $K_{\text{m}}$.

\subsection{Phosphorylation as a Molecular Switch}

The complete dissociation induced by S305 phosphorylation ($\Delta G \approx 0$) positions this modification as a \textbf{binary on/off switch} for cGAS--TRIM41 interaction. The phosphoserine introduces both steric bulk and negative charge at the interface-proximal region, disrupting the electrostatic complementarity required for binding.

The phosphomimetic S305E shows heterogeneous behavior (one replica dissociated, two bound), indicating that \textbf{charge alone is insufficient} to fully recapitulate phosphorylation. The phosphate group's rigid geometry and additional hydrogen-bonding capacity (relative to glutamate) likely contribute to the deterministic dissociation. This has implications for therapeutic design: phosphomimetics may not faithfully reproduce phospho-regulation.

\subsection{Cross-Species Conservation and Divergence}

The Hgal system is currently under simulation. Preliminary docking results suggest that naked mole-rat cGAS adopts a more compact N-terminal geometry (18.4\,\AA{} active-site spread vs 28.6\,\AA{} in human), which may naturally favor tighter TRIM41 engagement. The reverse mutant (Hgal\_4mut\_rev) is predicted to partially restore the human-like dispersed geometry, providing an elegant reciprocal validation of our allosteric model.

\subsection{Limitations and Future Directions}

\textbf{Methodological limitations}: (1) MM-GBSA absolute values are unreliable for protein-protein interactions; we report them for comparative purposes only. (2) The 200\,ns simulation time may be insufficient to capture rare dissociation events for tightly bound systems. (3) Our models lack the full-length TRIM41 (only SPRY domain was simulated); the RING domain may introduce additional conformational constraints. (4) No explicit membrane or DNA was included, which may affect cGAS conformation in vivo.

\textbf{Future work}: (1) Umbrella sampling along the COM reaction coordinate to compute the full PMF and extract dissociation rates. (2) HDX-MS predictions to identify dynamic hotspots. (3) In vitro ubiquitination assays with purified proteins to validate the ``binding-tolerant but catalysis-optimized'' model. (4) Cryo-EM of the cGAS--TRIM41 complex to resolve the binding interface at atomic resolution.

\section{Methods}

\subsection{Sequence Preparation and Structure Prediction}

Human cGAS (UniProt: Q8N884, 522 aa) and naked mole-rat cGAS (UniProt: A0AAX6RS70, 554 aa) sequences were retrieved from UniProt. The four variant positions were mapped through global pairwise alignment (Biopython pairwise2, gap open $-10$, gap extend $-0.5$): human 463$\rightarrow$479$\rightarrow$495$\rightarrow$498 corresponds to naked mole-rat 463$\rightarrow$511$\rightarrow$527$\rightarrow$530. TRIM41 (UniProt: Q8WV44, 630 aa) was modeled with AlphaFold3; the SPRY domain (residues 413--630) was used for docking and MD due to low confidence in the N-terminal RING-Bbox-coiled-coil regions.

\subsection{Protein-Protein Docking}

\textbf{LightDock} (v0.9.4) was used with the fastdfire scoring function. Setup: 20 swarms $\times$ 20 glowworms, 100 simulation steps, default restraints. \textbf{Rosetta docking\_protocol} (2026.15) used the ref2015 scoring function with nstruct = 10 decoys per system.

\subsection{Molecular Dynamics Simulations}

All MD simulations used \textbf{OpenMM 8.5.1} with the \textbf{Amber ff19SB} force field and \textbf{OPC} water model. Systems were solvated in truncated octahedron boxes with 10\,\AA{} buffer, neutralized with Na$^+$/Cl$^-$ (0.15\,M). Production runs used LangevinMiddleIntegrator (300\,K, 1.0/ps friction, 2\,fs timestep) with HBonds constraints, PME for electrostatics, and 1.0\,nm nonbonded cutoff. Three independent replicas were run per system (different random seeds).

\textbf{Simulated systems}: Hsap\_WT (3$\times$200\,ns), Hsap\_4mut (3$\times$200\,ns), Hsap\_WT\_S305phos (3$\times$200\,ns), Hsap\_WT\_S305E (3$\times$200\,ns), Hgal\_WT (3$\times$200\,ns, in progress), Hgal\_4mut\_rev (3$\times$200\,ns, in progress).

\textbf{GROMACS validation}: A subset of replicas was also run with GROMACS 2026.0 (CUDA, Amber force field native implementation) for cross-engine validation.

\subsection{MM-GBSA Calculations}

MM-GBSA binding free energies were computed with MMPBSA.py (AmberTools 24) using the GB5 model (igb=5, saltcon=0.150\,M). Trajectories were subsampled every 50 frames. Complex, receptor, and ligand prmtop files were generated with ante-MMPBSA.py. Protein-only NetCDF trajectories were extracted from full-system DCD using MDAnalysis.

\subsection{Analysis}

\textbf{COM distance}: Mass-weighted center of mass of cGAS CA atoms vs TRIM41 CA atoms. \textbf{H-bonds}: MDAnalysis HydrogenBondAnalysis (donor--acceptor cutoff 3.5\,\AA, angle 150$^\circ$). \textbf{RMSF}: Per-residue CA RMSF after alignment to the first frame. \textbf{Clustering}: Gaussian Mixture Model (scikit-learn) with BIC model selection on COM + RMSD + R$_g$ features. \textbf{DCCM}: Dynamic cross-correlation matrix from aligned CA trajectories.

\section{Data and Code Availability}

All simulation trajectories, analysis scripts, and raw data are available at [PLACEHOLDER --- GitHub repository URL upon publication]. Key scripts: \path{scripts/02_md/run_production.py} (OpenMM MD), \path{scripts/03_analysis/analyze_s305e.py} (S305E analysis), \path{scripts/03_analysis/delta_rmsf.py} ($\Delta$RMSF), \path{scripts/03_analysis/delta_dccm.py} ($\Delta$DCCM).

\begin{acknowledgement}
[PLACEHOLDER]
\end{acknowledgement}

\begin{suppinfo}
\begin{itemize}
\item Figure S1: Sequence alignment of human and naked mole-rat cGAS
\item Figure S2: AF3 prediction quality maps
\item Figure S3: LightDock pose validation
\item Figure S4: Per-residue displacement maps
\item Figure S5: Cluster time evolution
\item Figure S6: GROMACS vs OpenMM cross-validation
\item Table S1: Full MD simulation parameters
\item Table S2: Complete MM-GBSA per-replica results
\end{itemize}
\end{suppinfo}

\begin{thebibliography}{9}
\bibitem{longevity-review} [PLACEHOLDER --- Naked mole-rat longevity review]
\bibitem{chen2025} Chen et al.~(2025). \textit{A cGAS-mediated mechanism in naked mole-rats potentiates DNA repair and delays aging}. Science. [PLACEHOLDER --- full citation]
\bibitem{cgas-review} [PLACEHOLDER --- cGAS-STING pathway review]
\bibitem{cgas-dna-repair} [PLACEHOLDER --- cGAS in DNA repair]
\bibitem{trim41-review} [PLACEHOLDER --- TRIM41 E3 ligase characterization]
\bibitem{genheden2015} Genheden, S. \& Ryde, U.~(2015). The MM/PBSA and MM/GBSA methods to estimate ligand-binding affinities. \textit{J.\ Chem.\ Inf.\ Model.}, 55(5), 1046--1061.
\bibitem{allostery-e3} [PLACEHOLDER --- Allostery in E3 ligases]
\end{thebibliography}

\end{document}
